% ============================================================
% main.tex
% VVUQ-05 full-bill (LaTeX)
%   H. R. 9510 BILL v3.0 - THE VISUAL AMENDMENT to the Federal Food, Drug, and
%   Cosmetic Act (21 U.S.C. 301 et seq.), grounded on the Title 21 device
%   provisions current through Public Law 119-93.
%
% WHAT THIS FILE IS. This is the finished v3.0 visual bill for H. R. 9510,
% produced from the VVUQ-05 draft-bill scaffold by executing every bracketed
% drafting instruction against the named figures-bill, next-steps, and VVUQ-04
% final-bill sources. The drafting-instruction blocks and figure slots are gone;
% every figure and table is rendered, and the operative text of Bill v2.0 (the
% VVUQ-04 final-bill) is carried so the bill stands on its own. It keeps the full
% congressional amendment structure (caption; A BILL; enacting clause; SECTION 1
% short title and a clickable, page-filling table of contents; SEC. 2 findings;
% SEC. 3 the operative amendment and new section 515D; SEC. 4 comparative print)
% and adds five non-operative appendices that carry the visual, deliverable, and
% explainability perspective: Appendix A visualizes the VVUQ-01 and VVUQ-02
% engineering evidence; Appendix B catalogs every required submission deliverable;
% Appendix C establishes the VVUQ-01 through VVUQ-04 developments as an
% explainability standard; Appendix D is the research-influence matrix; and
% Appendix E is the development-transparency statement and commit schedule.
%
% Compile recipe (Overleaf, pdfLaTeX):
%   pdflatex main.tex
%   bibtex   main
%   pdflatex main.tex
%   pdflatex main.tex
%
% Formatting (centralized in usctitle.sty): white background throughout;
% RaggedRight body with even interword spacing and no right-margin overflow;
% maximal widow and orphan penalties so no single line is stranded; an
% abbreviated running header with no overlapping fields; URL breaking in the
% references; single hyphens only; the section symbol for every codified
% reference; full-width left-aligned ragged-right tables; and ASCII figures set
% verbatim in white, black-ruled monospace frames that are centered on the page
% and sized to their content, so they render as they would in a fenced GitHub
% Markdown block.
% ============================================================
\documentclass[11pt]{article}
\usepackage{usctitle}

\title{Verification Before Generation in Physical AI Oncology Trials Act of 2026
(H. R. 9510), Bill v3.0: A Visual Amendment to the Federal Food, Drug, and
Cosmetic Act}
\author{Prepared for VVUQ-05 by CEO Kevin Kawchak, ChemicalQDevice}
\date{June 4, 2026 (current through Public Law 119-93)}

\begin{document}

% ============================================================
% BILL CAPTION AND FRONT MATTER (the caption page). The House and Senate
% statements are condensed: the long title appears once, the referral block is
% brief, and the standard enacting clause is retained. A centered ASCII overview
% of the v3.0 visual process closes the page.
% ============================================================
\thispagestyle{plain}
\pagenumbering{roman}

\billcaption{119TH CONGRESS}{2d Session}{H.\,R. 9510}

\billlongtitle{To amend the Federal Food, Drug, and Cosmetic Act to require an
automated verification, validation, and uncertainty quantification process to
clear robot-patient interaction code before that code is generated or executed
in a Physical AI oncology clinical investigation.}

\billintro{IN THE HOUSE OF REPRESENTATIVES}{June 4, 2026}{%
Mr.\ \underline{Kevin Kawchak} authored the following bill with the assistance of
artificial intelligence; which was referred to the Committee on Energy and
Commerce.}

\billhead

\enactingclause

\billcovernote{\href{https://doi.org/10.5281/zenodo.20535429}{Bill (v3.0) 10.5281/zenodo.20535429} is the visual amendment of H. R. 9510, the Verification
Before Generation in Physical AI Oncology Trials Act of 2026. It renders eleven text figures and ten full-width tables, a visual
engineering-evidence appendix, a submission-deliverables appendix, and an
explainability-standard appendix. It was prepared with the assistance of an
autonomous artificial intelligence coding agent (Claude Code Opus 4.8, 1M
context, Max) under human direction. It is an independent research draft, is not
an enacted law, and is not legal advice; the development record appears in
Appendix E.}

\begin{asciifig}
EVIDENCE (VVUQ-01, VVUQ-02)         LAW (VVUQ-03 bill, VVUQ-04 amendment) 
+----------------------------+      +-----------------------------------+
| method + 51-test pipeline  | ===> | H. R. 9510 standalone bill        |
| 10-gate humanoid, 172 test |      | FD&C Act amendment, new 360e-5    |
+----------------------------+      +-----------------------------------+
              |                                       |
              +-------------------+-------------------+
                                  v
            VVUQ-05/update-bill  (the inputs to this bill)
            +---------------------------------------------+
            | figures-bill : every ASCII diagram + table  |
            | next-steps   : the submission deliverables  |
            +---------------------------------------------+
                                  |
                                  v
           H. R. 9510 BILL v3.0  <== THIS VISUAL AMENDMENT
           figures and tables rendered; deliverables written
                                  |
                                  v
           the final visual bill (this PDF) and the
           papers/VVUQ-05/full-bill/deliverables package
\end{asciifig}
\vspace{-0.4cm}
\figcaption{Cover Figure. The Bill v3.0 visual process: VVUQ-01 through VVUQ-04
evidence and law, reorganized through the VVUQ-05 update-bill inputs into this
finished visual amendment and its submission-deliverables package.}



% \clearpage
\pagenumbering{arabic}

% ============================================================
% SECTION 1. SHORT TITLE; TABLE OF CONTENTS.
% The table of contents is clickable (each entry links to its section) and is
% set to fill the remainder of the page with evenly distributed leaders.
% ============================================================
\billsec{SECTION 1.}{SHORT TITLE; TABLE OF CONTENTS.}\phantomsection\label{toc:s1}

\uscprov{1}{\textbf{(a) Short Title.} This Act may be cited as the
``Verification Before Generation in Physical AI Oncology Trials Act of 2026''.}

\uscprov{1}{\textbf{(b) Table of Contents.} The table of contents for this Act version is
as follows. Each entry links to the part it names.}

\vspace{0.5\baselineskip}
\billtoc{%
\billtocline{toc:s1}{Sec.~1.}{Short title; table of contents.}{The citation of
the Act and this clickable contents.}
\vfill
\billtocline{toc:s2}{Sec.~2.}{Findings; the evidence to law record.}{Why the
verify-before-generate rule is needed and feasible, with the four-work record.}
\vfill
\billtocline{toc:s3}{Sec.~3.}{Amendment to the Federal Food, Drug, and Cosmetic
Act.}{The new section 515D (21 U.S.C. 360e-5) and ten conforming amendments.}
\vfill
\billtocline{toc:s4}{Sec.~4.}{Comparative print; changes in existing law.}{The
eleven affected Title 21 device sections, marked.}
\vfill
\billtocline{toc:a5}{App.~A.}{Visual engineering evidence (non-operative).}{The
VVUQ-01 and VVUQ-02 record the findings rest on.}
\vfill
\billtocline{toc:a6}{App.~B.}{Required submission deliverables
(non-operative).}{The package a House office expects before introduction.}
\vfill
\billtocline{toc:a7}{App.~C.}{The VVUQ explainability standard
(non-operative).}{How the legislation-creation process is made inspectable.}
\vfill
\billtocline{toc:a8}{App.~D.}{Research influence matrix (non-operative).}{Emerging
bills and executive actions, kept out of the operative text.}
\vfill
\billtocline{toc:a9}{App.~E.}{Development transparency and commit
schedule.}{How Bill v3.0 was built across a single pull request.}
}
\vspace{10cm}


% ============================================================
% BILL BODY AND APPENDICES (one file per section; each corresponds to main.tex).
% The bill body (SEC. 2 through SEC. 4) carries the operative text, the rendered
% findings and amendment visuals, and the comparative print; the appendices carry
% the visual, deliverable, and explainability perspective. Each file opens with
% its own heading and renders its figures and tables on a white background.
% ============================================================
\input{sections/s2-findings}
\input{sections/s3-amendment}
\input{sections/s4-comparative}
\input{sections/a5-evidence}
\input{sections/a6-deliverables}
\input{sections/a7-explainability}
\input{sections/a8-research-matrix}
\input{sections/a9-transparency}

% ============================================================
% AUTHORSHIP, NOTICES, AND PROVENANCE.
% ============================================================
% \clearpage
\vspace{0.5cm}
\phantomsection
\addcontentsline{toc}{section}{Authorship, Notices, and Provenance}
\usccrosshead{AUTHORSHIP, NOTICES, AND PROVENANCE}

\uscnotepar{Prepared by CEO Kevin Kawchak
(\href{https://orcid.org/0009-0007-5457-8667}{ORCID 0009-0007-5457-8667}),
ChemicalQDevice (\href{mailto:kevink@chemicalqdevice.com}{kevink@chemicalqdevice.com}).
Adapted using Claude Code Opus 4.8 (1M context) Max; research assisted by ChatGPT
and Google Gemini.}

\uscnotepar{Notice: This measure was adapted from documents of the United States
Government in the public domain under 17 U.S.C. 105. The reproduced statutory
text is in the public domain; the authoritative version is the United States Code
as published by the Office of the Law Revision Counsel. This work is not endorsed
or sponsored by the FDA, HHS, the OLRC, CFR, ICH, or any member of Congress.}

\uscnotepar{Disclaimer: This work is an independent research draft, is not an
enacted law, and is not legal advice; it is not endorsed, sponsored, or approved
by any trial sponsor, contract research organization, site, institutional review
board, regulator, or medical society. All supporting numbers are simulation or
illustrative results from the seed 20260525, and no
patient-identifiable information is included.}

\uscnotepar{Rights: The reproduced statutory text is in the public domain; the
generated amendment framing, figures, tables, and notices are released under the
Creative Commons Attribution 4.0 International License (CC BY 4.0),
\href{https://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.}

\href{https://doi.org/10.5281/zenodo.20535429}{DOI current bill (v3.0): 10.5281/zenodo.20535429}

\href{https://doi.org/10.5281/zenodo.20485580}{DOI prior bill (v2.0): 10.5281/zenodo.20485580}

\href{https://doi.org/10.5281/zenodo.20331505}{DOI repository: 10.5281/zenodo.20331505}

\uscnotepar{San Diego. June 4, 2026.}

% ============================================================
% PROVENANCE AND RESEARCH SOURCES (BIBLIOGRAPHY).
% A real congressional bill carries no bibliography; this research-aid back
% matter does, so the operative text stays clean while sources remain auditable.
% ============================================================
\clearpage
\phantomsection
\addcontentsline{toc}{section}{Provenance and Research Sources}
\usccrosshead{Provenance and Research Sources}
\vspace{-0.6cm}

\begingroup
\RaggedRight
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{references}
\endgroup

\end{document}
