% Back matter: Acknowledgments, Ethical Disclosures, Rights and Permissions,
% Cite This Article, Data Availability (final content, wording preserved), and
% the Stakeholder Register (built from the policy-memo groups).




\vspace{-0.1cm}

\phantomsection
% \addcontentsline{toc}{section}{Acknowledgments}
\section*{Acknowledgments}
\label{sec:acknowledgments}
\vspace{-0.15cm}
The author would like to acknowledge Anthropic for providing access to Claude
Code for the bill preparation process; and also recognition to OpenAI ChatGPT, Claude Haiku, and Google Gemini for research assistance.
 
 
\vspace{-0.1cm}
\phantomsection
% \addcontentsline{toc}{section}{Ethical Disclosures}
\section*{Ethical Disclosures}
\label{sec:ethics}
\vspace{-0.15cm}
The author of the article declares no competing interests. This is an independent
draft and is not endorsed, sponsored, or approved by any trial sponsor, CRO, site,
IRB, regulator, or medical society, nor by CFR, ICH, or FDA. All supporting
numbers are simulation results, and the Unitree H2-Surgical 1.0 is a clearly
labelled hypothetical 2030 platform.
\vspace{-0.1cm}
\phantomsection
\addcontentsline{toc}{section}{Rights and Permissions}
\section*{Rights and Permissions}
\label{sec:rights}
\vspace{-0.15cm}
This article is distributed under the terms of the Creative Commons Attribution
4.0 International License (CC BY 4.0), which permits unrestricted use,
distribution, and reproduction in any medium, provided the original author and
source are properly credited, a link to the Creative Commons license is provided,
and any modifications made are indicated. To view a copy of this license, visit
\url{https://creativecommons.org/licenses/by/4.0/}. This draft was adapted from
original CFR documents in the public domain under 17 U.S.C. \S~105.
\vspace{-0.1cm}
\phantomsection
\addcontentsline{toc}{section}{Cite This Article}
\section*{Cite This Article}
\label{sec:cite}
\vspace{-0.15cm}
Kawchak K. VVUQ Physical AI Oncology Trial Bill. Zenodo. 2026;
\href{https://doi.org/10.5281/zenodo.20454870}{10.5281/zenodo.20454870}.
\vspace{-0.1cm}
\phantomsection
\addcontentsline{toc}{section}{Data Availability}
\section*{Data Availability}
\label{sec:data}
\vspace{-0.15cm}
All scaffolding, instructions, and supporting records for this new bill are openly
available in the \texttt{kevinkawchak/cancer-automated} GitHub repository under
\texttt{papers/VVUQ-03/full-paper/} and \texttt{papers/VVUQ-03/draft-paper/},
with the supporting VVUQ-01 and VVUQ-02 records under \texttt{papers/VVUQ-01/}
and \texttt{papers/VVUQ-02/}, and are archived on Zenodo. The national platform,
USL, and PSL records are in the sibling repository
\texttt{kevinkawchak/physical-ai-oncology-trials}
(\href{https://doi.org/10.5281/zenodo.19244918}{10.5281/zenodo.19244918}). All
data sets are synthetic or illustrative and reproducible from the deterministic
seed 20260525 described in the supporting records; no patient-identifiable
information is included.

\vspace{-0.1cm}
\phantomsection
\addcontentsline{toc}{section}{Stakeholder Register}
\section*{Stakeholder Register}
\label{sec:stakeholders}
\vspace{-0.15cm}
The bill is written to serve the groups named in the policy memorandum, each with
a distinct interest that a specific section addresses, and it carries the
national platform's patient-empowerment framing that the patient, not the vendor
or the payer, is the party the verification gate protects
\cite{kawchak2026national}. Table~\ref{tab:stakeholders} ties each stakeholder to
its interest and to the section that answers it.

\clearpage

\begin{table}[ht]
\centering
\begin{tabularx}{\textwidth}{L{4cm} Y L{4.5cm}}
\toprule
\textbf{Stakeholder} & \textbf{Interest} & \textbf{Relevant section} \\
\midrule
Health systems & Throughput, safety, and cost of Physical AI trials & Implementation and fiscal \\
Clinicians & Retained medical-necessity decision and human oversight & Statutory § 7; attestations \\
Patients and disability-rights groups & Nondiscrimination, accessibility, and empowerment \cite{usc-ada, usc-titlevi} & Nondiscrimination § 8 \\
AI developers & A clear, automatable verify-before-generate rule & Statutory § 3 and § 4 \\
Payers & Medical-necessity and utilization-review alignment & Prior-law crosswalk \\
Device makers & Documentation and USL readiness standard & Documentation § 6; readiness § 5 \\
Regulators & Auditable credibility and oversight authority & Oversight and enforcement \\
\bottomrule
\end{tabularx}
\caption{Stakeholder register: interests tied to the bill section that addresses them.}
\label{tab:stakeholders}
\end{table}

