% ============================================================
% main.tex
% VVUQ-05 draft-bill (LaTeX)
%   H. R. 9510 BILL v3.0 - a VISUAL DRAFT amendment to the Federal Food, Drug,
%   and Cosmetic Act (21 U.S.C. 301 et seq.), grounded on the Title 21 device
%   provisions current through Public Law 119-93.
%
% WHAT THIS FILE IS. This is the v3.0 visual scaffold for H. R. 9510. It is NOT
% a finished bill. It keeps the full congressional amendment structure of Bill
% v2.0 (the VVUQ-04 final-bill: caption, A BILL, enacting clause, SECTION 1 short
% title and table of contents, SEC. 2 findings, SEC. 3 the operative amendment
% and new section 515D, SEC. 4 comparative print) so it stands on its own as a
% bill, and it ADDS a more visual perspective: every operative part carries a
% figure or table slot and a set-off DRAFTING INSTRUCTIONS block that tells a
% future Claude Code Opus 4.8 (1M context) Max pass exactly which files in this
% repository to process to render that figure or table on a white background as
% a text-based diagram, with no raster image. Five non-operative appendices
% extend the perspective: Appendix A visualizes the VVUQ-01 and VVUQ-02
% engineering evidence; Appendix B instructs the build of every required U.S.
% Bill submission deliverable; Appendix C establishes the VVUQ-01 through VVUQ-04
% developments as a new standard for explainability of the legislation-creation
% process; Appendix D is the research-influence matrix; and Appendix E is the
% development-transparency statement and commit schedule.
%
% WHY A VISUAL PERSPECTIVE. Bill v3.0 answers three goals. First, it is a
% visualization of Bill v2.0, built on the VVUQ-01 through VVUQ-04 record and the
% verbatim visual catalog in papers/VVUQ-05/update-bill/figures-bill. Second, it
% scaffolds the supplementary Markdown deliverables that papers/VVUQ-05/update-
% bill/next-steps says a U.S. House bill needs before submission, to be added in
% a later step under papers/VVUQ-05/deliverables. Third, it establishes the
% four-work evidence-to-law pipeline as a reusable explainability standard. The
% bill is separately compiled in LaTeX into a PDF; the deliverables are separate
% Markdown documents, each complete and submission quality at this bill version.
%
% Compile recipe (Overleaf, pdfLaTeX):
%   pdflatex main.tex
%   bibtex   main
%   pdflatex main.tex
%   pdflatex main.tex
%
% Formatting (centralized in usctitle.sty): white background throughout;
% RaggedRight body with even interword spacing and no right-margin overflow;
% maximal widow and orphan penalties so no single line is stranded; an
% abbreviated running header with no overlapping fields; URL breaking in the
% references; single hyphens only; the section symbol for every codified
% reference; full-width left-aligned ragged-right tables; and ASCII figures set
% verbatim in white, black-ruled monospace frames that preserve spacing exactly.
% ============================================================
\documentclass[11pt]{article}
\usepackage{usctitle}

\title{Verification Before Generation in Physical AI Oncology Trials Act of 2026
(H. R. 9510), Bill v3.0: A Visual Draft Amendment to the Federal Food, Drug, and
Cosmetic Act}
\author{Prepared for VVUQ-05 by CEO Kevin Kawchak, ChemicalQDevice}
\date{June 3, 2026 (current through Public Law 119-93)}

\begin{document}

% ============================================================
% BILL CAPTION AND FRONT MATTER (the caption page). The House and Senate
% statements are condensed: the long title appears once, the referral block is
% brief, and the standard enacting clause is retained. An ASCII overview of the
% v3.0 visual draft process closes the page.
% ============================================================
\thispagestyle{plain}
\pagenumbering{roman}

\billcaption{119TH CONGRESS}{2d Session}{H.\,R. 9510}

\billlongtitle{To amend the Federal Food, Drug, and Cosmetic Act to require an
automated verification, validation, and uncertainty quantification process to
clear robot-patient interaction code before that code is generated or executed
in a Physical AI oncology clinical investigation.}

\billintro{IN THE HOUSE OF REPRESENTATIVES}{June 3, 2026}{%
Mr. \underline{Kevin Kawchak} authored the following bill with the assistance of
artificial intelligence; which was referred to the Committee on Energy and
Commerce}

\billhead

\enactingclause

\billcovernote{Bill v3.0 is a visual draft of H. R. 9510, the Verification
Before Generation in Physical AI Oncology Trials Act of 2026. It keeps the full
operative text of Bill v2.0 so it stands on its own, and it adds a visual
perspective: figure and table slots, an engineering-evidence appendix, a
submission-deliverables appendix, and an explainability-standard appendix. It
was prepared with the assistance of an autonomous artificial intelligence coding
agent (Claude Code Opus 4.8, 1M context, Max) under human direction. It is an
independent research draft, is not an enacted law, and is not legal advice; the
development record appears in Appendix E.}

\begin{asciifig}
  EVIDENCE (VVUQ-01, VVUQ-02)         LAW (VVUQ-03 bill, VVUQ-04 amendment)
  +----------------------------+      +-----------------------------------+
  | method + 51-test pipeline  |      | H. R. 9510 standalone bill        |
  | 10-gate humanoid, 172 test | ===> | FD&C Act amendment, new 360e-5    |
  +----------------------------+      +-----------------------------------+
               |                                       |
               +------------------+--------------------+
                                  v
             VVUQ-05/update-bill  (the inputs to this draft)
             +---------------------------------------------+
             | figures-bill : every ASCII diagram + table  |
             | next-steps   : the submission deliverables  |
             +---------------------------------------------+
                                  |
                                  v
         H. R. 9510 BILL v3.0   <== THIS VISUAL DRAFT SCAFFOLD
         bracketed instructions name the exact files to process
                                  |
                                  v
         A future Claude Code pass renders the figures and the
         deliverables, yielding the final visual bill and the
         papers/VVUQ-05/deliverables submission package
\end{asciifig}
\figcaption{Cover Figure. The Bill v3.0 visual draft process: VVUQ-01 through
VVUQ-04 evidence and law, reorganized through the VVUQ-05 update-bill inputs into
this scaffold, then rendered by a future pass into the final bill and the
deliverables package.}

\clearpage
\pagenumbering{arabic}

% ============================================================
% SECTION 1. SHORT TITLE; TABLE OF CONTENTS.
% ============================================================
\billsec{SECTION 1.}{SHORT TITLE; TABLE OF CONTENTS.}

\uscprov{1}{\textbf{(a) Short Title.} This Act may be cited as the
``Verification Before Generation in Physical AI Oncology Trials Act of 2026''.}

\uscprov{1}{\textbf{(b) Table of Contents.} The table of contents for this Act is
as follows:}

\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.9\linewidth}@{}}
Sec. 1. Short title; table of contents.\\
Sec. 2. Findings; the evidence to law record.\\
Sec. 3. Amendment to the Federal Food, Drug, and Cosmetic Act.\\
Sec. 4. Comparative print; changes in existing law.\\
Appendix A. Visual engineering evidence (non-operative).\\
Appendix B. Required submission deliverables (non-operative).\\
Appendix C. The VVUQ explainability standard (non-operative).\\
Appendix D. Research influence matrix (non-operative).\\
Appendix E. Development transparency and commit schedule.\\
\end{tabular}
\end{center}

\begin{draftbox}{Section 1 - short title and table of contents}
\dstep{Retain the short title verbatim from papers/VVUQ-04/final-bill/main.tex (SECTION 1(a)); verify the bill name and the Act name against papers/VVUQ-04/instruct-bill/10-legal-crosswalk-and-bill-style.md (Section D and the drafting-conventions checklist in Section E, item 1: verify every bill and law name). Confirm H. R. 9510 and "119TH CONGRESS, 2d Session" against papers/VVUQ-04/final-bill/README.md.}
\dstep{Keep the table of contents as a single-column left-aligned list (the ragcol helper at width 0.9 of the line); list Sec. 1 through Sec. 4 and Appendix A through Appendix E exactly as above; keep each entry to one line and reword any wrap so no entry leaves a one- or two-word last line.}
\dstep{Do not number the new FD&C Act section here; the new section number (FD&C Act section 515D, 21 U.S.C. section 360e-5) is established in Sec. 3 and recorded in the clerical amendment to the Act's own table of contents.}
\end{draftbox}

% ============================================================
% BILL BODY AND APPENDICES (one file per section; each corresponds to main.tex).
% The bill body (SEC. 2 through SEC. 4) carries the operative text and the
% comparative print; the appendices carry the visual, deliverable, and
% explainability perspective. Each file opens with its own heading and ends with
% the DRAFTING INSTRUCTIONS that name the exact files a future pass must process.
% ============================================================
\input{sections/s2-findings}
\input{sections/s3-amendment}
\input{sections/s4-comparative}
\input{sections/a5-evidence}
\input{sections/a6-deliverables}
\input{sections/a7-explainability}
\input{sections/a8-research-matrix}
\input{sections/a9-transparency}

% ============================================================
% AUTHORSHIP, NOTICES, AND PROVENANCE.
% ============================================================
\clearpage
\phantomsection
\addcontentsline{toc}{section}{Authorship, Notices, and Provenance}
\usccrosshead{AUTHORSHIP, NOTICES, AND PROVENANCE}

\uscnotepar{Prepared by CEO Kevin Kawchak
(\href{https://orcid.org/0009-0007-5457-8667}{ORCID 0009-0007-5457-8667}),
ChemicalQDevice (\href{mailto:kevink@chemicalqdevice.com}{kevink@chemicalqdevice.com}).
Adapted using Claude Code Opus 4.8 (1M context) Max; research assisted by ChatGPT
and Google Gemini.}

\uscnotepar{Notice: This measure was adapted from documents of the United States
Government in the public domain under 17 U.S.C. 105. The reproduced statutory
text is in the public domain; the authoritative version is the United States Code
as published by the Office of the Law Revision Counsel. This work is not endorsed
or sponsored by the FDA, HHS, the OLRC, CFR, ICH, or any member of Congress.}

\uscnotepar{Disclaimer: This work is an independent research draft, is not an
enacted law, and is not legal advice; it is not endorsed, sponsored, or approved
by any trial sponsor, contract research organization, site, institutional review
board, regulator, or medical society. All supporting numbers are simulation or
illustrative results reproducible from the deterministic seed 20260525, and no
patient-identifiable information is included.}

\uscnotepar{Rights: The reproduced statutory text is in the public domain; the
generated amendment framing, figures, tables, and notices are released under the
Creative Commons Attribution 4.0 International License (CC BY 4.0),
\href{https://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.}

\href{https://doi.org/10.5281/zenodo.20485580}{DOI prior bill (v2.0): 10.5281/zenodo.20485580}

\href{https://doi.org/10.5281/zenodo.20372501}{DOI repository: 10.5281/zenodo.20372501}

\uscnotepar{San Diego. June 3, 2026.}

% ============================================================
% PROVENANCE AND RESEARCH SOURCES (BIBLIOGRAPHY).
% A real congressional bill carries no bibliography; this research-aid back
% matter does, so the operative text stays clean while sources remain auditable.
% ============================================================
\clearpage
\phantomsection
\addcontentsline{toc}{section}{Provenance and Research Sources}
\usccrosshead{Provenance and Research Sources}
\begingroup
\RaggedRight
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{references}
\endgroup

\end{document}
