% Results: the execution evidence and the figures. Instruction only.

[PROCESSING INSTRUCTION (Results). Report the executed evidence in five
short subsections that follow the execution record, then the per commit
processing evidence, then the figures. Report every number exactly as in
the execution files; do not round differently.

(1) Foundation and verification floor. 51 of 51 tests passed (0 skipped)
across 8 test modules; static analysis (ruff check, ruff format, yamllint)
clean. Render the per module counts (17, 8, 5, 5, 4, 4, 4, 4) as a table
from test-suite.md and reference it.

(2) Pipeline generation. Five deliverables completed all four stages; the
acceleration factor is 2.5 (30 baseline days to 12 automated days) from
the codegen formula automated\_days = 30.0 / (1.0 + runs * 0.5). Point to
the three saved artifacts (instructions.md, execution\_log.txt, paper.md).

(3) VVUQ gate, the core result. Summarize the three shipped examples
(verification fraction 1.0; validation agreement 1.0 with worst relative
error 0.033 and human review recorded; uncertainty maximum CV 0.0068 over
3 runs, accepted). Then present the full decision surface in
Table~\ref{tab:results_gate}: 1 accept and 5 distinct blocks, 1 of which
escalates. Stress that a single failed check out of six dropped the
verification fraction to 0.83 and blocked case 6, which is the thesis in
one line.

(4) Stage 1 automation. Triple-run consensus converged (CV 0.0007 and
0.0001, 0 divergent); web search degraded gracefully to a labeled offline
stub after 4 bounded retries; the 200K chunker is byte-identical lossless
on line and ASCII paths; and one genuine limitation was found, a multibyte
hard-split that loses 6 characters at boundaries (carry this honestly into
Limitations). The scheduler planned 24 evenly spaced slots at 3600 s.

(5) Stage 2 reference. The 2030 PDAC hybrid pilot: a 60 second 8 arm
robotic Whipple on day 0 plus six 28 day Daraxonrasib adjuvant cycles
through day 168 (7 timeline events, human oversight required). The
lights-off controller emergency-stops over budget faults and blocks on an
unsatisfied interlock; note that vvuq\_gate\_online is one of the four
default interlocks, wiring Stage 1 assurance into Stage 2 safety.

(6) Per commit processing evidence. Present the execution commit metrics
in Table~\ref{tab:results_exec_commits} and reproduce the ASCII commit
timeline as a figure; use it to argue that real time, per commit LLM VVUQ
processing scales in practice, a concrete advantage over prior batch
systems.

SOURCE FILES:

\begin{table}[H]
\caption{Results source map (abbreviated paths under repo root).}
\label{tab:results_sources}
\centering
\begin{tabular}{L{4.7cm} L{8.7cm}}
\toprule
\textbf{Source (under repo root)} & \textbf{Use for} \\
\midrule
  execution/01-foundation/ : test-suite.md & 51 of 51 tests, 8 module counts, the verbatim roster. \\
  execution/02-pipeline/ : README + 3 artifacts & Five deliverables, the 2.5x factor, the three generated artifacts. \\
  execution/03-vvuq/ : README.md & Examples 1 to 3 and the full 6 case gate decision surface. \\
  execution/04-stage1-automation/ : README + chunk artifact & Simulation, ingestion, chunking, scheduler outcomes and the multibyte finding. \\
  execution/05-physical-ai-stage2/ : README + PDAC timeline & PDAC pilot timeline and the lights-off safety surface. \\
\bottomrule
\end{tabular}
\end{table}

SOURCE DATA to render as publication tables (numbers are fixed):

\begin{table}[H]
\caption{The full VVUQ gate decision surface (1 accept, 5 block, 1 escalate).}
\label{tab:results_gate}
\centering
\begin{tabular}{C{0.6cm} L{4.6cm} C{1.5cm} C{1.4cm} L{4.0cm}}
\toprule
\textbf{\#} & \textbf{Scenario} & \textbf{Accept} & \textbf{Escal.} & \textbf{Blocking reason} \\
\midrule
  1 & clean, human reviewed, low CV & yes & no & none \\
  2 & no human review recorded & no & no & human review not recorded \\
  3 & divergent runs, high CV & no & yes & max cv 0.365 above 0.1 \\
  4 & observed disagrees with reference & no & no & agreement 0.00; rel err 0.600 \\
  5 & only 2 runs, need 3 & no & no & only 2 runs, need 3 \\
  6 & artifact exceeds 200K cap & no & no & verification fraction 0.83 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Autonomous execution commits producing the run record.}
\label{tab:results_exec_commits}
\centering
\begin{tabular}{C{0.6cm} L{1.9cm} L{4.8cm} C{1.5cm} C{1.6cm}}
\toprule
\textbf{\#} & \textbf{Hash} & \textbf{Section} & \textbf{Lines} & \textbf{Time (UTC)} \\
\midrule
  1 & d7721a7 & Foundation (env, tests, lint) & +387 & 04:20:42 \\
  2 & b146ef7 & Pipeline (five methods) & +322 & 04:22:43 \\
  3 & c340cef & VVUQ (gate surface) & +223 & 04:24:05 \\
  4 & f5cb95b & Stage 1 automation & +238 & 04:26:26 \\
  5 & 2eb5cf0 & Physical-AI Stage 2 (PDAC) & +176 & 04:27:42 \\
  6 & ddd41e9 & Comprehensive README & +401/-1 & 04:32:08 \\
  7 & 9437292 & Fix errors (2nd to last) & +7/-6 & 04:35:34 \\
  8 & 57aa8db & Repository updates (last) & +102/-13 & 04:38:44 \\
\bottomrule
\end{tabular}
\end{table}

Reproduce the ASCII commit timeline (UTC, commit, section, delta, gap)
from the task's EXECUTION COMMIT PROCESSING block inside a verbatim figure
so the cadence is visible at a glance.

FIGURES from imagegen Python data (use the .py scripts for the data
literals, never the .png files; do not use the image-instruct directory;
only these four figures are in scope here):

\begin{table}[H]
\caption{Results figures grounded in imagegen Python scripts.}
\label{tab:results_figs}
\centering
\begin{tabular}{L{4.8cm} L{8.6cm}}
\toprule
\textbf{Script dir (under imagegen/)} & \textbf{Render as} \\
\midrule
  02-acceleration-waterfall/ *.py & A schedule waterfall, 30 to 12 days via reductions 10, 5, 3; reproduce the audit formula. \\
  04-vvuq-assurance-wheel/ *.py & A radar wheel of the six normalized assurance spokes against the threshold ring. \\
  06-test-coverage-treemap/ *.py & A treemap of 51 of 51 tests across the 8 modules (areas 17, 8, 5, 5, 4, 4, 4, 4). \\
\bottomrule
\end{tabular}
\end{table}

HOW TO PROCESS: pull the numeric arrays from each script's literals and
either redraw the figure or tabulate the data; cite the figure, do not
restate it in prose. Keep subsections tight and let
Tables~\ref{tab:results_gate} and~\ref{tab:results_exec_commits} carry the
detail. Cite \cite{repo-cancer-automated}, \cite{sel2025vvuq}, and
\cite{kawchak2025pdactwin} where the evidence connects to the literature.]
