%% ============================================================
%% sections/a8-research-matrix.tex
%% H. R. 9510 Bill v3.0 - APPENDIX D. RESEARCH INFLUENCE MATRIX (NON-OPERATIVE).
%% The 119th Congress emerging bills and the executive actions, kept out of the
%% operative text and confined to this matrix, a memo, testimony, or the findings
%% narrative. Rendered visual: Table 8 (the research influence matrix).
%% ============================================================
% \clearpage
\phantomsection\label{toc:a8}
\addcontentsline{toc}{section}{Appendix D. Research Influence Matrix (Non-Operative)}
\usccrosshead{APPENDIX D. RESEARCH INFLUENCE MATRIX (NON-OPERATIVE)}

\uscprov{1}{The authorities in this appendix are research influences only. They
inform the legislative findings, a policy memorandum, testimony, and this matrix,
but none is cited as the legal basis of an operative clause of this Act. Only
enacted statutes, in-force rules, and recognized standards carry operative weight,
so the 119th Congress emerging bills and the executive actions are kept here and
out of the bill text, consistent with the operative-versus-influence rule the
prior bill follows \cite{kawchak2026vvuq04bill}. Each entry is verified by number,
subject, and status before use; for example, there is no VALID Act in the 119th
Congress, so none is cited.}

{\footnotesize
\begin{xltabular}{\textwidth}{@{}L{2.0cm} L{4.2cm} Y L{2.4cm}@{}}
\hline\noalign{\vskip 0.04cm}
\textbf{Authority} & \textbf{What it is} & \textbf{What it informs} &
\textbf{Placement}\\
\hline\noalign{\vskip 0.04cm}
\endfirsthead
\hline\noalign{\vskip 0.04cm}
\textbf{Authority} & \textbf{What it is} & \textbf{What it informs} &
\textbf{Placement}\\
\hline\noalign{\vskip 0.04cm}
\endhead
\hline\noalign{\vskip 0.04cm}
\endlastfoot
EO 14179 & Removing Barriers to American Leadership in AI (90 FR 8741) &
Deregulatory posture in findings narrative \cite{eo-14179} & Memo; matrix\\
\hline\noalign{\vskip 0.04cm}
EO 14365 & National Policy for AI & State-law review and
preemption context \cite{eo-14365} & Appendix; matrix\\
\hline\noalign{\vskip 0.04cm}
OMB M-25-21 & Accelerating Federal Use of AI & Pre-deployment testing analogue
\cite{omb-m2521} & Memo; matrix\\
\hline\noalign{\vskip 0.04cm}
HHS AI & The HHS A.I. Strategy, 12/2025 &
Governance and reproducibility framing \cite{hhs-ai-strategy-2025} & Memo;
matrix\\
\hline\noalign{\vskip 0.04cm}
H.R. 238 & Healthy Technology Act of 2025 & AI prescribing-authority direction
\cite{hr238-healthy-tech} & Testimony; matrix\\
\hline\noalign{\vskip 0.04cm}
S. 1399 & Health Tech Investment Act & Medicare payment-class direction
\cite{s1399-health-tech-investment} & Testimony; matrix\\
\hline\noalign{\vskip 0.04cm}
H.R. 6361 & Ban AI Denials in Medicare Act & Human-over-AI signal
\cite{hr6361-ban-ai-denials} & Find. narr.; matrix\\
\hline\noalign{\vskip 0.04cm}
H.R. 5045 & HEALTH AI Act & Generative-AI research direction
\cite{hr5045-health-ai} & Memo; matrix\\
\hline\noalign{\vskip 0.04cm}
H.Res. 694 & Sense of House: CMS WISeR & Countervailing
human-review signal \cite{hres694-wiser} & Find. narr.; matrix\\
\hline
\end{xltabular}}
\vspace{-0.8cm}
\figcaption{Table 8. Research influence matrix: each research-influence authority,
what it is, what it informs in the bill package, and its placement (memo,
appendix, testimony, or this matrix). No row is cited from an operative clause.}

\uscprov{1}{The placement column is kept consistent with the testimony and
research-influence brief among the deliverables, so the same authority carries the
same placement in both; the operative sections and the comparative print remain
free of these authorities \cite{vvuq05-next-steps}.}
