% Back matter: Acknowledgments, Ethical Disclosures, Rights and Permissions,
% Cite This Article, Data Availability. Final content (not an instruction block);
% the wording is kept as given.

\phantomsection
\addcontentsline{toc}{section}{Acknowledgments}
\section*{Acknowledgments}
\label{sec:acknowledgments}
\vspace{-0.15cm}
The author would like to acknowledge Anthropic for providing access to Claude
Code for instruction, code, execution, along with the paper generation process;
OpenAI for providing access to ChatGPT for subject support, and Google
Gemini AI Overview for additional search assistance.

\vspace{-0.1cm}

\phantomsection
\addcontentsline{toc}{section}{Ethical Disclosures}
\section*{Ethical Disclosures}
\label{sec:ethics}
\vspace{-0.15cm}
The author of the article declares no competing interests.

\vspace{-0.1cm}

\phantomsection
\addcontentsline{toc}{section}{Rights and Permissions}
\section*{Rights and Permissions}
\label{sec:rights}
\vspace{-0.15cm}
This article is distributed under the terms of the Creative Commons Attribution
4.0 International License (CC BY 4.0), which permits unrestricted use,
distribution, and reproduction in any medium, provided the original author(s) and
source are properly credited, a link to the Creative Commons license is provided,
and any modifications made are indicated. To view a copy of this license, visit
\url{https://creativecommons.org/licenses/by/4.0/}.

\vspace{-0.1cm}

\phantomsection
\addcontentsline{toc}{section}{Cite This Article}
\section*{Cite This Article}
\label{sec:cite}
\vspace{-0.15cm}
Kawchak K. Mobile Pancreatic Cancer Unitree H2 Surgical Humanoid with Priority VVUQ. Zenodo. 2026;
\href{https://doi.org/10.5281/zenodo.20421754}{10.5281/zenodo.20421754}.

\vspace{-0.1cm}

\phantomsection
\addcontentsline{toc}{section}{Data Availability}
\section*{Data Availability}
\label{sec:data}
\vspace{-0.15cm}
All code, configuration, execution records, and figure scripts supporting this
manuscript are openly available in the \texttt{kevinkawchak/cancer-automated}
repository under \texttt{papers/VVUQ-02/} (inputs, codegen, execution, imagegen,
and this final paper), and are archived on Zenodo. The raw level-0 humanoid sensor
stream is deposited to Zenodo and referenced by per-iteration pointer files rather
than committed. All datasets are synthetic or illustrative and reproducible from
the deterministic seed 20260525 described in the Methods section; no patient-identifiable
information is included.
