% Limitations and Future Work: honest prose with one supporting table. The thesis
% depends on honest VVUQ, so every gap is stated plainly and none of the steps
% that could not be run are omitted.

The thesis depends on honest verification, validation, and uncertainty
quantification, so this section states every gap plainly. None of the steps that
could not be run is omitted or quietly approximated, and the future work follows
directly from closing those gaps.

\subsection{Limitations and approximations}

Several capabilities were deliberately or necessarily not exercised live, and
each is recorded with the module it affects and its mitigation in
\autoref{tab:limitations}. The on-prem language-model backends were not installed
and no key was present, so the autonomy intent module and the comparison judge
ran on their deterministic offline paths; this is the guarded
continuous-integration behavior and the correct default, but the live agentic
authoring and judging paths were not executed here. Live Zenodo deposition was
not performed, so the patcher wrote pointer JSON with placeholder hashes against
an absent staging directory rather than depositing the level-0 stream; the
pointer and manifest logic ran fully, only the network deposition did not. There
was no MuJoCo, NVIDIA Isaac, ROS 2, graphics processor, or display in the
container, so the behavior models are analytic standard-library references and no
physics-backed or rendered simulation ran; these are planning and assurance
references, not a robot controller. 

The committed sensor sample is only the first
50 ms of the 60-second timeline, since 500 ticks at the 10 kHz command rate sit
entirely in phase 1 with a single grasp state, and the full stream of roughly
600,000 ticks per hand is the Zenodo level-0 deposit, by design not committed.
Local execution used a single Python, 3.11.15, with cross-version coverage on
3.10, 3.11, and 3.12 delegated to the integration matrix rather than a local
multi-version run. The paper templates were intentionally not processed. And the
H2-Surgical 1.0 is a hypothetical 2030 device, so every number is a simulation
result and the four-entrant comparison is simulation against simulation.

\begin{table}[H]
\caption{Limitations and mitigations; affected module leaf names under the common
parent \texttt{papers/VVUQ-02/codegen/src/}.}
\label{tab:limitations}
\centering
\footnotesize
\begin{tabularx}{\textwidth}{Y L{4.1cm} Y}
\toprule
\textbf{Limitation} & \textbf{Affected module (leaf)} & \textbf{Mitigation and status} \\
\midrule
On-prem LLM backends not installed & \texttt{autonomy/llm\_intent.py}, \texttt{llm/compare\_agent.py} & ran the deterministic offline path, the guarded CI behavior \\
Live deposition not performed & \texttt{zenodo/patch\_pointers.py} & pointer, manifest logic ran; placeholder hashes; no net. deposit \\
No physics or robotics backend & analytic behavior models & planning and assurance references; physics deferred to future work \\
Committed sample is the first 50 ms & \texttt{sensors/ingest\_h2.py} & full 60 s stream is the Zenodo level-0 deposit, not committed \\
Single local Python version (3.11.15) & whole tree & cross-version coverage delegated to the CI matrix (3.10, 3.11, 3.12) \\
Paper templates not processed & \texttt{templates/Template\_04/} & out of scope by instruction \\
Simulation-only platform & all entrants & every number is a simulation result; simulation vs.\ simulation \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Future work}

The tractable next step is to adapt this ten-gate, standards-anchored humanoid
VVUQ automation across all oncology clinical trial deliverables, as speed, quality, and cost benefits here generalise. Each new deliverable
inherits the same scaffold: a reproducible determinism floor from a fixed seed, a
pass-or-fail verification gate, validation against independent references, a
first-class uncertainty bound with an escalate path, and a runtime binding to
published standards, so a sponsor adopting it does not re-derive the assurance
argument. From this simulation-only reference the path forward
is to add physics-backed and live-backend runs, MuJoCo or NVIDIA Isaac for
contact dynamics, on-prem language-model intent and judging, and real Zenodo
deposition of the level-0 stream, and then to assemble the regulatory artifacts: conformance to IEC 80601-2-77 and IEC 60601,
ISO 13482, an FDA SaMD Class III
submission, IRB
approval, and regulatory authorization \cite{iec8060127, iec60601, iso13482,
fda2023credibility}. This connects directly to the author's fully automated sponsor and the federated multi-site
layer \cite{kawchak2026sponsor, kawchak2026federated}, and it frames the
opportunity squarely: U.S. leadership in surgical-humanoid VVUQ tied to
external standards would advance patient safety, efficacy, and trial speed.
