% Conclusions and Effective Date. Built by the future pass from the instructions
% below. Do not process now. Restates the thesis as a legislative conclusion and
% sets the effective-date and enactment clause. Keep it tight; no new evidence.

[Write two or three connected paragraphs and a short effective-date clause. Do not
introduce new data; conclude from what the findings established. Synthesise the
conclusions of the two prior studies, do not quote them at length.]

[Paragraph 1, The legislative conclusion. Restate the thesis as the operative
conclusion: because the assurance process, not code generation, is the
substantial and decision-bearing work, a law that requires the VVUQ verification
process to clear ahead of code generation is the appropriate instrument to protect
patient safety and efficacy in Physical AI oncology trials. Tie this to the
recorded evidence by reference (the gate, not generation, decided in VVUQ-01; the
assurance suite outweighed the control code in VVUQ-02) and to the dual-layer USL
and PSL readiness gate. Source from
\texttt{VVUQ-01/final-paper/sections/conclusions.tex} and
\texttt{VVUQ-02/final-paper/sections/conclusions.tex}. Cite
\texttt{kawchak2026vvuq01} and \texttt{kawchak2026vvuq02}.]

[Paragraph 2, The national claim. State, respectfully and opportunistically, that
codifying verification before generation, bound to external standards, keeps the
United States first in surgical-humanoid VVUQ while making oncology trials faster,
less expensive, and safer, consistent with the 2026 FDA real-time clinical trials
initiative; keep mentions of the FDA and other bodies non-presumptuous. Cite
\texttt{fda2026realtime} and \texttt{fda2023credibility}.]

[Effective-date clause. Add a short clause: the Act takes effect on a stated day
after enactment (for example, the first day of the first calendar quarter
beginning at least one year after the date of enactment), with the readiness-gate
and documentation duties phased per
\texttt{sections/implementation\_enforcement.tex}. Cross-reference that section
rather than repeating its schedule.]
