% Supporting Documentation Referenced (Not Physically Attached). MAIN POINT 4,
% required. Built by the future pass from the instructions below. Do not process
% now. This section lists the supporting materials the bill relies on but does
% not attach, with a stable path and DOI for each, per the policy-development
% guidance that executable code, model weights, training data sets, and Git
% repositories are referenced rather than filed.

[Open with a short paragraph stating the principle: consistent with how
legislation is assembled, the bill references its supporting documentation rather
than physically attaching it, because executable code, model weights, training
data sets, and Git repositories are not appropriate attachments to a statute; they
are deposited, versioned, and citable. Each referenced item must be reachable by a
repository path and a resolvable DOI or URL. Then carry the inventory in one
referenced-documentation table; do not narrate it row by row.]

[Build the referenced-documentation table with columns for the artifact, its
repository path (abbreviated leaf, parent path given once at the top of each
block), its DOI or URL by bibliography key, and the reason it is referenced rather
than attached. Populate it from the records below, and feature the two large data
artifacts again in this not-attached context so the reader sees they are
deposited, not pasted into the bill.]

[Block 1, VVUQ-02 codegen and data (referenced, not attached). The generated code
tree and its documentation under \texttt{papers/VVUQ-02/codegen/} (src, config,
docs, schemas, tests); the four-entrant tournament
\texttt{papers/VVUQ-02/codegen/results/comparison.json} (1790 lines); the humanoid
sensor stream \texttt{papers/VVUQ-02/codegen/data/sample\_h2\_sensor.csv} (1001
lines, 27 columns, non-repetitive), its companion
\texttt{sample\_h2\_sensor.jsonl}, and \texttt{human\_surgeon\_baseline.csv}; and
the decision record \texttt{results/vvuq\_decisions.json}. Note that the raw
level-0 humanoid sensor stream is deposited to Zenodo and referenced by per-
iteration pointer files under \texttt{codegen/data/iterations/} rather than
committed, exactly the deposit-and-reference pattern the bill prescribes. Cite
\texttt{kawchak2026vvuq02} and \texttt{repo-cancer-automated}.]

[Block 2, VVUQ-02 and VVUQ-01 execution records (referenced, not attached). The
five-section VVUQ-02 execution record under \texttt{papers/VVUQ-02/execution/}
(foundation, pipeline, vvuq, automation, humanoid-deployment) and its README, and
the VVUQ-01 execution record under \texttt{papers/VVUQ-01/execution/} (the five
numbered sections). These are the run logs and artifacts that evidence the
attestations; they are referenced so a reviewer can reproduce, not re-litigate,
the runs. Cite \texttt{kawchak2026vvuq01}.]

[Block 3, National-platform documentation package (referenced, not attached). Use
the national-platform \texttt{source\_documents.tex} catalog and
\texttt{appendices.tex} (Appendix A source-files directory and Appendix C cross-
reference matrix) as the model for how a comprehensive documentation package is
referenced from a single instrument, and reference the USL and PSL standards and
the site documentation package by DOI. Cite \texttt{kawchak2026national},
\texttt{kawchak2026sitedocs}, and \texttt{kawchak2026mcp}.]

[Close with the deposit-and-reference rule the bill adopts: each supporting
artifact must carry a resolvable DOI and a repository URL (GitHub and Zenodo), be
versioned, and be reproducible from a stated seed, so that the not-attached
documentation is nonetheless fully auditable. Cross-reference
\texttt{sections/algorithm\_documentation.tex} (which features the same two data
artifacts as filed documentation) and \texttt{sections/attestations\_compliance.tex}
(which relies on these records as evidence). Cite \texttt{zenodo}.]

% Model referenced-documentation table (parent paths at top, abbreviated leaves):
% \begin{table}[h]\centering
% \begin{tabularx}{\textwidth}{L{4.6cm} L{2.8cm} Y}
% \toprule
% \textbf{Artifact (abbreviated leaf)} & \textbf{Reference} & \textbf{Why referenced, not attached} \\
% \midrule
% \multicolumn{3}{l}{\textit{Parent: papers/VVUQ-02/codegen/}} \\
% results/comparison.json & kawchak2026vvuq02 & 1790-line result file; deposited and versioned \\
% data/sample\_h2\_sensor.csv & kawchak2026vvuq02 & 1001-row data set; not a statutory attachment \\
% src/, config/, tests/ & repo-cancer-automated & Executable code and configuration; referenced \\
% \multicolumn{3}{l}{\textit{Parent: physical-ai .../final\_paper/sections/}} \\
% source\_documents.tex & kawchak2026national & Model for referencing a documentation package \\
% \bottomrule
% \end{tabularx}
% \caption{Supporting documentation referenced by path and DOI, not physically attached.}
% \end{table}
