% Conclusions and Effective Date. Two connected paragraphs of conclusion and a
% short effective-date clause. No new data; the conclusion follows from the
% findings already established.

The conclusion of this bill follows from its findings rather than from any new
evidence. Because the assurance process, not code generation, is the substantial
and decision-bearing work, a law that requires the VVUQ verification process to
clear ahead of code generation is the appropriate instrument to protect patient
safety and efficacy in Physical AI oncology trials. The recorded evidence carries
this conclusion: in the first study the gate, not the generation, decided which
artifact could proceed, and in the second study the assurance suite outweighed
the control code in the test budget \cite{kawchak2026vvuq01, kawchak2026vvuq02}.
The dual-layer readiness gate reinforces it, because the Physical AI Standard
Level verifies the site and the Unification Standard Level validates the robot,
so the code-level gate never stands alone.

Codifying verification before generation, bound to external standards, keeps the
United States first in surgical-humanoid VVUQ while making oncology trials faster,
less expensive, and safer. This posture is consistent with the 2026 real-time
clinical trials initiative, which automated assurance makes feasible rather than
constrains, and with the agency credibility framework the gate is designed to
support \cite{fda2026realtime, fda2023credibility}. The references to the Food and
Drug Administration and to other bodies throughout this bill are respectful and
non-presumptuous: the instrument is offered to advance the field and to help the
country lead it, not to bind any agency to a result.

\subsection{Effective Date}

(a) \textit{In general.} This Act shall take effect on the first day of the first
calendar quarter beginning at least one year after the date of enactment.

(b) \textit{Phasing.} The readiness-gate and documentation duties shall be phased
in accordance with Section~\ref{sec:implementation_enforcement}, and that
schedule is not restated here.
